True versus apparent shapes of bow shocks and bow waves

### 2017-11-05 papers/Paper1/sec-conic.tex
Make start on describing projected quadric figures

%The transformation between the conic parameters and the characteristic radii are given by:
%\begin{align}
%R_c &= \frac{b^2}{a} \\
%R_{90} &= b\left[\pm\left(1 - \frac{(a \mp R_0)^2}{a^2}\right)\right]^{1/2}\label{eq:r90-conic}
%\end{align}ut 
%In (\ref{eq:r90-conic}), the positive sign correspond to an elliptic quadric, while the negative sign to an hyperbolic quadric.
%The inverse transformation of (\ref{eq:Rc-conic}) and (\ref{eq:r90-conic}) is given by:
%\begin{align}
%\frac{a}{R_0} &= \frac{A}{2A-B^2} \label{eq:a-conic}\\
%\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}}\\
%\tan\theta_c &= \frac{2A-B^2}{\left|B^2 - 2A\right|^{1/2}} \label{eq:thc-conic} \\
%\mathrm{where:~} B &\equiv \frac{R_{90}}{R_0} \\
%#A &\equiv \frac{R_c}{R_0}
%\end{align}
\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \begin{tabular}{@{}ll@{}}
    (a) & (b) \\
    \includegraphics{figs/projected-Rc-vs-i}
        & \includegraphics{figs/projected-R0-vs-i} \\
    (c) & (d) \\
    \includegraphics{figs/projected-R90-vs-i}
    & \includegraphics{figs/projected-R90-vs-Rc}
  \end{tabular}
  \caption[]{Effects of projection on quadrics of revolution:
    variation with inclination of bow size and shape.  Different line
    colors correspond to varying quadric parameter, \(\Q\), (see key),
    while variation in line width corresponds to variation in the
    ``true'' planitude, \(\Pi\), or apex radius of curvature. Vertical
    gray rectangles show quartiles of \(|\sin i|\), which will be
    equally populated for an isotropic distribution of
    orientations. (a)~Projected planitude: \(\Pi'\). (b)~Projected/true
    star-apex distance: \(R_0' / R_0\).  (c)~Projected alatude:
    \(\Lambda'\). (d)~Diagnostic diagram for
    dimensionless projected radii: \(\tilde{R}_{90}'\) versus
    \(\tilde{R}_c'\).  Shading indicates different classes of
    quadrics: hyperboloids (white), prolate spheroids (dark gray), and
    oblate spheroids (light gray), with the limiting case of
    paraboloids shown by the thin black line.}
  \label{fig:quadric-projection}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
  \caption{Variation with inclination angle of projected quadric parameters}
  \label{fig:projected-R90-Rc-snapshots}
\end{figure*}

@@

The projection of the apex distance then follows from the primed
version of equation~\eqref{eq:R0-from-Q-a-x0} as
\begin{equation}
  \label{eq:R0-prime}
  \frac{R_0'}{R_0} =
  \cos i \left[ 1 + \frac{\Pi} {\Q} \bigl(\fQi - 1\bigr) \right]
\end{equation}
and the projected planitude and alatude can be calculated as
\begin{align}
  \label{eq:Pi-prime}
  \Pi' &= \frac{\Pi}{(R_0'/R_0)\, \fQi \cos i } \\
  \label{eq:Lambda-prime}
  \Lambda' &= \left( 2 \Pi' - \Q' \right)^{1/2} \ .
\end{align}

>>>>

%The transformation between the conic parameters and the characteristic radii are given by:
%\begin{align}
%R_c &= \frac{b^2}{a} \\
%R_{90} &= b\left[\pm\left(1 - \frac{(a \mp R_0)^2}{a^2}\right)\right]^{1/2}\label{eq:r90-conic}
%\end{align}ut 
%In (\ref{eq:r90-conic}), the positive sign correspond to an elliptic quadric, while the negative sign to an hyperbolic quadric.
%The inverse transformation of (\ref{eq:Rc-conic}) and (\ref{eq:r90-conic}) is given by:
%\begin{align}
%\frac{a}{R_0} &= \frac{A}{2A-B^2} \label{eq:a-conic}\\
%\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}}\\
%\tan\theta_c &= \frac{2A-B^2}{\left|B^2 - 2A\right|^{1/2}} \label{eq:thc-conic} \\
%\mathrm{where:~} B &\equiv \frac{R_{90}}{R_0} \\
%#A &\equiv \frac{R_c}{R_0}
%\end{align}
\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \begin{tabular}{@{}ll@{}}
    (a) & (b) \\
    \includegraphics{figs/projected-Rc-vs-i}
        & \includegraphics{figs/projected-R0-vs-i}
  \end{tabular}
  \caption[]{Effects of projection on quadrics of revolution:
    variation with inclination of bow size and shape.  Different line
    colors correspond to varying quadric parameter, \(\Q\), (see key),
    while variation in line width corresponds to variation in the
    ``true'' planitude, \(\Pi\), or apex radius of curvature. Vertical
    gray rectangles show quartiles of \(|\sin i|\), which will be
    equally populated for an isotropic distribution of
    orientations. (a)~Projected planitude: \(\Pi'\). (b)~Projected/true
    star-apex distance: \(R_0' / R_0\). }
  \label{fig:quadric-projection}
\end{figure*}

@@

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \begin{tabular}{@{}ll@{}}
    (a) & (b) \\
    \includegraphics{figs/projected-R90-vs-i}
    & \includegraphics{figs/projected-R90-vs-Rc}
  \end{tabular}
  \caption[]{As Figure~\ref{fig:quadric-projection}, but (a)~projected
    alatude, \(\Lambda'\), versus inclination, \(i\), and (b)~diagnostic
    planitude--alatude diagram: \(\Lambda'\) versus \(\Pi'\).  Shading
    indicates different classes of quadrics: hyperboloids (white),
    prolate spheroids (dark gray), and oblate spheroids (light gray),
    with the limiting case of paraboloids shown by the thin black
    line.}
  \label{fig:quadric-projection-continued}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/projected-R90-Rc-snapshots}
  \caption{Variation with inclination angle of the apparent shape of
    quadric bows.  Upper left panel shows a set of quadrics at zero
    inclination, uniformly distributed in planitude and alatude in the
    ranges \(\Pi = [\frac12, 7]\), \(\Lambda = [\frac12, 7]\).  Subsequent
    panels show the effect of projection on the apparent
    \((\Pi', \Lambda')\) as the inclination is increased from
    \(0^\circ\) to \(80^\circ\) in \(10^\circ\) steps.}
  \label{fig:projected-R90-Rc-snapshots}
\end{figure*}

The projection of the apex distance then follows from the primed
version of equation~\eqref{eq:R0-from-Q-a-x0} as
\begin{equation}
  \label{eq:R0-prime}
  \frac{R_0'}{R_0} =
  \cos i \left[ 1 + \frac{\Pi} {\Q} \bigl(\fQi - 1\bigr) \right]
\end{equation}
and the projected planitude and alatude can be calculated as
\begin{align}
  \label{eq:Pi-prime}
  \Pi' &= \frac{\Pi}{(R_0'/R_0)\, \fQi \cos i } \\
  \label{eq:Lambda-prime}
  \Lambda' &= \left( 2 \Pi' - \Q' \right)^{1/2} \ .
\end{align}
These are all shown in Figures~\ref{fig:quadric-projection}
and~\ref{fig:quadric-projection-continued} for a variety of quadric
parameter \(Q\) (line color) and true planitude \(\Pi\) (line
thickness).  The projected planitude and alatude
(Figs~\ref{fig:quadric-projection}a and
\ref{fig:quadric-projection-continued}a) behave in a qualitatively
similar fashion.  Whatever the true values of \(\Pi\) and \(\Lambda\), all
spheroids (\(\Q > 0\)) tend towards \(\Pi' = 1\) and \(\Lambda' = 1\) as the
inclination increases towards \(90^\circ\).  This is because when the
spheroid is oriented edge-on, we see its circular cross-section.
Hyperboloids, on the other hand,

Paraboloids (\(\Q = 0\)), on the other hand,
